Dish: Distribution-oblivious Shell Scripting

### 2020-02-25 pldi/draft.tex
Change format to ACM small for ICFP
Notes on plan

%% For double-blind review submission, w/o CCS and ACM Reference (max submission space)
\documentclass[sigplan,10pt,review,anonymous]{acmart}
\settopmatter{printfolios=false,printccs=false,printacmref=false}
%% For double-blind review submission, w/ CCS and ACM Reference
%\documentclass[sigplan,review,anonymous]{acmart}\settopmatter{printfolios=true}
%% For single-blind review submission, w/o CCS and ACM Reference (max submission space)
%\documentclass[sigplan,review]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
%% For single-blind review submission, w/ CCS and ACM Reference
%\documentclass[sigplan,review]{acmart}\settopmatter{printfolios=true}
%% For final camera-ready submission, w/ required CCS and ACM Reference
%\documentclass[sigplan]{acmart}\settopmatter{}

@@

>>>>

%% For double-blind review submission, w/o CCS and ACM Reference (max submission space)
% Limit: 25 pages
% https://icfp20.sigplan.org/track/icfp-2020-papers#Call-for-Papers
\documentclass[acmsmall,10pt,review,anonymous]{acmart}
\settopmatter{printfolios=false,printccs=false,printacmref=false}
%% For double-blind review submission, w/ CCS and ACM Reference
%\documentclass[sigplan,review,anonymous]{acmart}\settopmatter{printfolios=true}
%% For single-blind review submission, w/o CCS and ACM Reference (max submission space)
%\documentclass[sigplan,review]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
%% For single-blind review submission, w/ CCS and ACM Reference
%\documentclass[sigplan,review]{acmart}\settopmatter{printfolios=true}
%% For final camera-ready submission, w/ required CCS and ACM Reference
%\documentclass[sigplan]{acmart}\settopmatter{}

@@

\nv{I don't think the intro needs any serious rewrite, apart from deleting any
notion of distribution and highlighting parallel processing.

Key tasks, in rough order of importance:
  (i) change title and intro to avoid distribution
  (ii) cleanup and rewrite sections 4, 5: introduce our high-level figure, talk
  about things in order, add ordering in graphs, generally refine and beautify
  as much as possible.
  (iii) tighten section 2, everything in there has to be related to some part of
  the story---make the connection explicit
  (iv) Pump up evaluation: could we add 3 more micro-benchmarks? could we add
  1--2 more macro-benchmarks?
  (v) since this is IFCP, could we add some simple semantics and derivation
  rules? we should certainly be able to describe some of the optimizations as
  congruence rules.
  (vi) complete the related work with some operating-systems literature.
}
